\documentclass[a4paper,man,natbib,floatsintext,12pt]{apa7}

\usepackage[english]{babel} %character and hyphenation rules specific to the language you choose
%\usepackage[utf8x]{inputenc}
\usepackage{graphicx}
\usepackage{color}
\usepackage{tikz}
\usepackage{amsmath}
\usepackage{blindtext}
\usepackage{tabularx} %great for APA-style Tables
\usepackage{siunitx} % Required for good table alignmen
\sisetup{
  round-mode          = places, % Rounds numbers
  round-precision     = 2, % to 2 places
}
\usepackage{multirow}
\usepackage{booktabs}
\usepackage{wrapfig}
\usetikzlibrary{shapes,decorations,arrows,calc,arrows.meta,fit,positioning}
\tikzset{
    -Latex,auto,node distance =1 cm and 1 cm,semithick,
    latent/.style ={ellipse, draw, minimum width = 0.7 cm},
    observed/.style ={rectangle, draw},
    bidirected/.style={Latex-Latex,dashed},
    el/.style = {inner sep=2pt, align=left, sloped}
}
\newcommand{\sigFtest}[4]{\textit{F}(#1,#2) = #3, \textit{p}$<$#4}
\newcommand{\nonsigFtest}[3]{\textit{F}(#1,#2) = #3, \textit{p}$>$.05}


\title{Impact of Mask Use on Facial Emotion Recognition in Individuals with Subclinical Social Anxiety: An Eye-tracking Study}
\shorttitle{SOCIAL ANXIETY AND MASKS ON FACIAL EMOTION RECOGNITION }
\author{Jackie Wai Yi Wo}
\affiliation{Department of Psychology, The University of Hong Kong, Hong Kong SAR, China}
\journal{Cognitive Research: Principles and Implications}
\abstract{Previous studies suggested that social anxiety is associated with theory of mind deficit and eye gaze avoidance when identifying facial emotions. We tested the hypothesis that socially anxious individuals would be more affected by mask use during facial emotion recognition. Eighty-eight healthy undergraduates with various levels of social anxiety were invited. Participants judged the emotions of masked and unmasked facial expressions. Eye Movement Analysis with Hidden Markov Models was used to analyze participants’ eye movement patterns during the task. Results failed to support our hypothesis. Instead, higher social anxiety was associated with higher hit rates for angry and fearful faces, regardless of mask use. Eye movement patterns were similar across social anxiety levels. Thus, our study indicates social anxiety, at least at subclinical levels, may be associated with a generally heightened sensitivity to negative emotions.}
\keywords{Social anxiety, Emotion recognition, Mask, Eye movement, EMHMM}
\authornote{The research presented in this assignment has been adapted from my published paper\citep{wo2025impact}. I acknowledge that the use of this material is solely for practicing LaTeX formatting, not for publishing original academic work.}
\leftheader{Alternate page header in man mode}

%-------------- END PREAMBLE  -------------------


\begin{document}

\maketitle  %Insert my APA style title page

\input{intro.tex}

\input{method.tex}

\input{results.tex}

\input{discussion.tex}


\bibliography{references.bib}

\end{document}